Usenet Project - CSV Cleaning

### 2024-09-01 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
added data

```{r Keyword Descriptive Statistics}
# Step 5: Group by newsgroup and calculate required statistics, including thread relevancy
keywords_summary_df <- comments_in_keyword_threads %>%
  group_by(newsgroup) %>%
  summarize(
    Comments_with_Keywords = sum(Relevancy > 0),
    Conversations_Mentioned_In = n_distinct(Thread.ID),
    Total_Comments_In_Threads = n(),
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
    Average_Relevancy_Score = mean(Relevancy, na.rm = TRUE)
  )

@@

# Add a totals row
totals <- keywords_summary_df %>%
  summarize(
    newsgroup = "Total",
    Comments_with_Keywords = sum(Comments_with_Keywords),
    Conversations_Mentioned_In = sum(Conversations_Mentioned_In),
    Total_Comments_In_Threads = sum(Total_Comments_In_Threads),
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
    Average_Relevancy_Score = mean(Average_Relevancy_Score, na.rm = TRUE),
    Average_Thread_Relevancy = mean(Average_Thread_Relevancy, na.rm = TRUE)
  )

>>>>

```{r Keyword Descriptive Statistics}
# Step 5: Group by newsgroup and calculate required statistics, including thread relevancy
keywords_summary_df <- comments_in_keyword_threads %>%
  group_by(newsgroup) %>%
  summarize(
    Unique_Authors = n_distinct(Author),
    Comments_with_Keywords = sum(Relevancy > 0),
    Conversations_Mentioned_In = n_distinct(Thread.ID),
    Total_Comments_In_Threads = n(),
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
    Average_Relevancy_Score = mean(Relevancy, na.rm = TRUE)
  )

@@

# Add a totals row
totals <- keywords_summary_df %>%
  summarize(
    newsgroup = "Total",
    Comments_with_Keywords = sum(Comments_with_Keywords),
    Conversations_Mentioned_In = sum(Conversations_Mentioned_In),
    Total_Comments_In_Threads = sum(Total_Comments_In_Threads),
    Unique_Authors = sum(Unique_Authors),
    Percent_Total_Comments_w_Keyword = (Comments_with_Keywords / Total_Comments_In_Threads) * 100,
    Average_Relevancy_Score = mean(Average_Relevancy_Score, na.rm = TRUE),
    Average_Thread_Relevancy = mean(Average_Thread_Relevancy, na.rm = TRUE)
  )
